### 2017-11-16 paper/sections/3_methodology.tex
paper: addresses #17, #25, and #31
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Mantle also provides functions for persisting state across decisions.
\texttt{WRState(s)} saves state \texttt{s}, which can be a number or boolean
value, and \texttt{RDState()} returns the state saved by a previous iteration.
For example, a ``when" policy can avoid trimming a cache or migrating data if
it had performed that operation in the previous decision using:

\begin{figure}[h]
\footnotesize
\begin{minted}{lua}
if RDState() == 1 then
  WRState(0)   -- the next decision will return true
  return false
else then
  WRState(1)   -- the next decision will return false
  return true
end
\end{minted}
\end{figure}

>>>>

Mantle also provides functions for persisting state across decisions.
\texttt{WRState(s)} saves state \texttt{s}, which can be a number or boolean
value, and \texttt{RDState()} returns the state saved by a previous iteration.
For example, a ``when" policy can avoid trimming a cache or migrating data if
it had performed that operation in the previous decision.

%\begin{figure}[h]
%\footnotesize
%\begin{minted}{lua}
%if RDState() == 1 then
%  WRState(0)   -- the next decision will return true
%  return false
%else then
%  WRState(1)   -- the next decision will return false
%  return true
%end
%\end{minted}
%\end{figure}

### 2017-11-16 paper/sections/4_dynamic-policies.tex
paper: addresses #17, #25, and #31
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

a\subsection{Trajectory Length}
%
%\subsection{Cloud Techniques: Elastic Search}
%
%What if we re-provision resources in response to events outside the
%application's control, such as a slow Lustre.
%
%\subsection{Future work}
%
%How Much: cache policy from past, regime detection, Belady's Min

@@

\section{Cache Management Using Domain-Specific Application Knowledge}
\label{sec:dom-specific}
\begin{figure}[t]
  \noindent\includegraphics[height=5cm,width=0.4\textwidth]{figures/keyspace-zoomed.png}\\

  \caption{Key activity for a 4 hour run shows groups of accesses to the same
  subset of keys. Detecting these access patterns leads to a more accurate cache
  management strategy.\label{fig:keyspace-zoomed}}

\end{figure}

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/dscache-vs-none.png}\\

\caption{The performance and resource utilization trade-off for the dynamically
sized cache (DSCache) policy compared to no cache management. With a negligible
performance impact, DSCache adjusts to different initial conditions
(\(\Delta\)) automatically and saves over 2\(\times\) memory in the best case.
\label{fig:dscache-vs-none}}
\end{figure}

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/memory-vs-time.png}\\

\caption{Memory utilization of different cache management policies.  ``No Cache
Management" allows unlimited cache growth, ``Multi-Policy" absorbs the initial
burstiness of the workload before switching to a more constrained cache, and
the ``Dynamic Policy" curves size the cache according to key access patterns.
We show a \(\Delta_2\) growth rate to demonstrate the dynamic policy's ability
to adjust to a different set of initial conditions.\label{fig:memory-vs-time}}
\end{figure}

@@

The performance and memory utilization is shown by the ``DSCache" bars in
Figure~\ref{dscache-vs-none.png}. Without sacrificing performance (trajectory
length), the dynamically sized cache policy uses between 32\%-66\% less memory
than the default ParSplice configuration (no cache management) for the 3
initial conditions we test. The memory usage is shown by the ``Dynamic Policy"
curves in Figure~\ref{figures/memory-vs-time.png}, where the behavior mirrors
the key access patterns in Figure~\ref{fig:keyspace-zoomed}.

@@

\begin{figure}[h]
\footnotesize
\begin{minted}[xleftmargin=3em,linenos]{lua}
d = timeseries()          -- data (d) provided by mantle
ts, id = d:get(d:size())  -- functions provided by mantle
fan  = {start=nil, finish=ts, top=0, bottom=id}
fans = {}
for i=d:size(),1,-1 do -- detect possible fans
  ts, id = d:get(i)
  if id < fan['bottom'] then
    fan['start']  = ts
    fans[#fans+1] = fan 
    fan = {start=nil, finish=ts, top=0, bottom=id}
  end

>>>>

\subsection{Trajectory Length}
%
%\subsection{Cloud Techniques: Elastic Search}
%
%What if we re-provision resources in response to events outside the
%application's control, such as a slow Lustre.
%
%\subsection{Future work}
%
%How Much: cache policy from past, regime detection, Belady's Min

@@

\section{Cache Management Using Domain-Specific Application Knowledge}
\label{sec:dom-specific}

\begin{figure*}[t!]
    \begin{subfigure}[t]{0.32\textwidth}
	\includegraphics[width=0.9\textwidth]{figures/keyspace-zoomed.png}\\
\caption{Key activity for a 4 hour run shows groups of accesses to the same
subset of keys. Detecting these access patterns leads to a more accurate cache
management strategy, which is discussed in
Section~\S\ref{sec:regime-detection}.\label{fig:keyspace-zoomed}}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.32\textwidth}
        \includegraphics[width=1\textwidth]{figures/memory-vs-time.png}\\
	\caption{Memory utilization for ``No Cache Management" (unlimited cache
growth), ``Multi-Policy" (absorbs initial burstiness of workload) , and
``Dynamic Policy" (sizes cache according to key access patterns).
\label{fig:memory-vs-time}}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.32\textwidth}
        \includegraphics[width=1\textwidth]{figures/dscache-vs-none.png}\\
	\caption{Performance/Utilization for dynamically sized cache (DSCache)
policy. With negligible performance degradation, DSCache adjusts to different
\(\Delta\)s over 2\(\times\) memory in the best case.
\label{fig:dscache-vs-none}}
    \end{subfigure}%
    \caption{Different cache management policies tested over the Mantle policy engine.}
\end{figure*}

%\begin{figure}[t]
%  \noindent\includegraphics[height=5cm,width=0.4\textwidth]{figures/keyspace-zoomed.png}\\
%
%  \caption{Key activity for a 4 hour run shows groups of accesses to the same
%  subset of keys. Detecting these access patterns leads to a more accurate cache
%  management strategy.\label{fig:keyspace-zoomed}}
%
%\end{figure}
%
%\begin{figure}[t]
%\noindent\includegraphics[width=0.5\textwidth]{figures/dscache-vs-none.png}\\
%
%\caption{The performance and resource utilization trade-off for the dynamically
%sized cache (DSCache) policy compared to no cache management. With a negligible
%performance impact, DSCache adjusts to different initial conditions
%(\(\Delta\)) automatically and saves over 2\(\times\) memory in the best case.
%\label{fig:dscache-vs-none}}
%\end{figure}
%
%\begin{figure}[t]
%\noindent\includegraphics[width=0.5\textwidth]{figures/memory-vs-time.png}\\
%
%\caption{Memory utilization of different cache management policies.  ``No Cache
%Management" allows unlimited cache growth, ``Multi-Policy" absorbs the initial
%burstiness of the workload before switching to a more constrained cache, and
%the ``Dynamic Policy" curves size the cache according to key access patterns.
%We show a \(\Delta_2\) growth rate to demonstrate the dynamic policy's ability
%to adjust to a different set of initial conditions.\label{fig:memory-vs-time}}
%\end{figure}

@@

The performance and memory utilization is shown by the ``DSCache" bars in
Figure~\ref{fig:dscache-vs-none}. Without sacrificing performance (trajectory
length), the dynamically sized cache policy uses between 32\%-66\% less memory
than the default ParSplice configuration (no cache management) for the 3
initial conditions we test. The memory usage is shown by the ``Dynamic Policy"
curves in Figure~\ref{fig:memory-vs-time}, where the behavior mirrors the key
access patterns in Figure~\ref{fig:keyspace-zoomed}. We also show a
\(\Delta_2\) growth rate to demonstrate the dynamic policy's ability to adjust
to a different set of initial conditions.

@@

\begin{figure}[h]
\footnotesize
\begin{minted}[xleftmargin=3em,linenos]{lua}
d = timeseries()          -- provided by mantle
ts, id = d:get(d:size())  -- provided by mantle
fan  = {start=nil, finish=ts, top=0, bottom=id}
fans = {}
for i=d:size(),1,-1 do    -- detect all fans
  ts, id = d:get(i)
  if id < fan['bottom'] then
    fan['start']  = ts
    fans[#fans+1] = fan 
    fan = {start=nil, finish=ts, top=0, bottom=id}
  end
